Titeln på avhandlingens språk

### 2022-08-19 publications/2021ImpactDelayedResponse/Response_to_Reviewers.tex

        \begin{revised}{596}{602}
            However, the present data provide relatively little support for these alternatives, in that the predicted measures did not produce the expected statistical trends.
            Specifically, physiological measures of GSR and HR failed to show evidence of differential arousal under long vs.\ short delays, and speed-induced errors and non-completions predicted by resource depletion were not observed.
            The acceleration data further did not indicate that extended delay significantly increases erratic movement.
        \end{revised}
    \end{answered}

\end{QandA}

\textit{Reviewer 2}
\begin{QandA}
    \item The explanations have been used too much in somewhere.
    For example, it is not necessary to explain the ANOVA test.
    This test is well known.

    \begin{answered}
        We agree with the reviewer.
        The explanation of the ANOVA test has been removed, and the paragraph has been reworked with a new reference:

        \begin{revised}{411}{413}
            We confirmed this effect through an \emph{analysis of variance} (ANOVA~\autocite{FUJIKOSHI1993ANOVA}) with factors of block length and delay, and found significant main effects of both factors and the interaction, shown in Table 2.
        \end{revised}

        We also understand this remark as relating to the same issues pointed out by \emph{Reviewer 1} in \labelcref{it:shorten31} and \labelcref{it:shorten333}.
        As such, we refer to our responses to these comments.
    \end{answered}

    \item Use more resolution for figures.

    \begin{answered}
        Yes, this has been addressed in the revised manuscript.
    \end{answered}

    \item Some figures can be inserted in a figure as subplots and or subpanels.

    \begin{answered}
        Agreed.
        This has been addressed in the revised manuscript.
        In particular, figure 4 has been reorganized and merged with figure 5 (in the old manuscript).
    \end{answered}

    \item In line 286 at the end of line the ``A Latin'' is written, what is that?

    \begin{answered}
        This is an artifact of the line-wrapping of the document.
        The segment of text actually reads ``A \emph{Latin~square}-type design [\ldots]'', but \LaTeX decided to automatically wrap the line right after \emph{Latin}.
        This has been fixed in the revised manuscript.
    \end{answered}

\end{QandA}

\pagebreak

\begingroup\setlength{\multicolsep}{0pt}
\begin{multicols}{2}[]
    \printbibliography[heading=letterbib]
\end{multicols}\endgroup
\end{letter}
\end{document}
